---
title: "Visualizing output from freeze-dryer"
author: "Casper Sahl Poulsen"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
always_allow_html: yes
output:
  pdf_document:
    toc: yes
    toc_depth: '5'
  html_document:
    toc: yes
    toc_depth: 5
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE, 
                      message = FALSE,
                      fig.align = "center")
```

## Introduction 
#### Study headline:
Visualize output from CoolSafe 9L Freeze-dryer https://www.labogene.com/CoolSafe-4-15L-Freeze-Dryers  
Freeze-drying: Primary drying 17h at 0.1hPa and 23 °C. Secondary drying 3h at 0.05hPa and 23 °C.

#### Background:  
In this context it is processing samples from the DCH-NG cohort (Investigations on the interaction between the microbiome, host genetic variation and life style in the development of type 2 diabetes, cardiovascular disease, liver disease and colorectal cancer) limited to MAX. 
Project F2: MAX samples where individuals have collected fecal samples at multiple time points, N=1319.   
Participant and study information is available in a separate document provided by KB.    
Sample aliquoting is performed from freeze-dried specimens. Sample aliquotation is not feasible using traditional laborious methods such as drilling.   

#### Aim:   
Visualize output, primarily investigate if freeze-drying is performing according to planned by achieving a steady temperature. 

### Packages  
```{r}

##mytree plotting
#library(data.tree) 
#library(plyr)

library(stringr)
library(ggplot2)
library(gridExtra)
```

### Reading in data
```{r eval=FALSE}
#path<-getwd()
#path2<-list.files(path, full.names = TRUE, recursive = TRUE)

#x <- lapply(strsplit(path, "/"), function(z) as.data.frame(t(z)))
#x <- rbind.fill(x)
#x$pathString <- apply(x, 1, function(x) paste(trimws(na.omit(x)), collapse="/"))
#(mytree <- data.tree::as.Node(x))
#mytree
#plot(mytree)

logCS <- read.delim(file="./RUN1/MAX F2 RUN1.csv", 
                       header=FALSE,
                       strip.white=TRUE,
                       sep = ";",
                       dec=",",
                       skip=11) #Maybe the skip changes between runs


names(logCS) <- lapply(logCS[2, ], as.character)
logCS<-logCS[-(1:2),]

names(logCS)<-str_replace(names(logCS), " ","_")

#Instead of using the datetime that has multiple of the same entries. 
#I'm using the log number instead .

##Remove unused columns
logCS<-logCS[,c(1,3,5,7,11:13)]

for (i in c(1,7)) {
  logCS[,i] <- as.numeric(as.character(logCS[,i]))
}

for (i in 2:6) {
  logCS[,i] <- as.numeric(gsub(",", ".", logCS[,i]))
} 

```

## Analyses
### Plot seperately
```{r eval=FALSE}


ggplot(logCS) + 
  geom_point(aes(LOG_nr, Shelf1, color="Shelf1"), size=1) + #color = Diagnosis, group = Diagnosis
  geom_point(aes(LOG_nr, Shelf3, color="Shelf2"), size=1) +
  geom_point(aes(LOG_nr, Shelf5, color="Shelf3"), size=1) +
  scale_color_manual(values=c(Shelf1 = "#0000FF", Shelf2 = "#FF0000",
                              Shelf3 = "#228B22")) +
  ggtitle("Shelf temperatures") + 
  xlab("Logging event") +
  ylab("Shelf / °C") +
  labs(color="") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        axis.title=element_text(size=12), legend.position="bottom")

ggplot(logCS[1:200,]) + 
  geom_point(aes(LOG_nr, Shelf1, color="Shelf1"), size=1) + #color = Diagnosis, group = Diagnosis
  geom_point(aes(LOG_nr, Shelf3, color="Shelf2"), size=1) +
  geom_point(aes(LOG_nr, Shelf5, color="Shelf3"), size=1) +
  scale_color_manual(values=c(Shelf1 = "#0000FF", Shelf2 = "#FF0000",
                              Shelf3 = "#228B22")) +
  ggtitle("Shelf temperatures first 200 events") + 
  xlab("Logging event") +
  ylab("Shelf / °C") +
  labs(color="") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        axis.title=element_text(size=12), legend.position="bottom")

ggplot(logCS) + 
  geom_point(aes(LOG_nr, Ice_condensor), size=1) + #color = Diagnosis, group = Diagnosis
  ggtitle("Ice condensor temperature") + 
  xlab("Logging event") +
  ylab("Ice condensor / °C") +
  labs(color="") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        axis.title=element_text(size=12), legend.position="bottom")

ggplot(logCS) + 
  geom_point(aes(LOG_nr, Product), size=1) + #color = Diagnosis, group = Diagnosis
  ggtitle("Product temperature") + 
  xlab("Logging event") +
  ylab("Product / °C") +
  labs(color="") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        axis.title=element_text(size=12), legend.position="bottom")

ggplot(logCS) + 
  geom_point(aes(LOG_nr, Actual_pressure), size=1) + #color = Diagnosis, group = Diagnosis
  ggtitle("Actual pressure") + 
  xlab("Logging event") +
  ylab("Pressure / XX") +
  labs(color="") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        axis.title=element_text(size=12), legend.position="bottom")
```


### Plot all runs 
```{r}
RunList <- list()
ShelfList <- list()
Shelf200List <- list()
ProductList <- list()
Product100List <- list()
IceConList <- list()
ActualPList <- list()
ActualPylimList <- list()

temp <- list.files(pattern="*.csv")
#myfiles = lapply(temp, read.delim)
All <- lapply(temp,function(i){
  read.delim(i, header=FALSE, strip.white=TRUE, sep = ";", dec=",", skip=11)
})

names(All) <- temp

for (j in 1:length(temp)) {
logCS <- All[[j]]

names(logCS) <- lapply(logCS[2, ], as.character)
logCS<-logCS[-(1:2),]

names(logCS)<-str_replace(names(logCS), " ","_")

#Instead of using the datetime that has multiple of the same entries. 
#I'm using the log number instead .

##Remove unused columns
logCS<-logCS[,c(1,3,5,7,11:13)]

for (i in c(1,7)) {
  logCS[,i] <- as.numeric(as.character(logCS[,i]))
}

for (i in 2:6) {
  logCS[,i] <- as.numeric(gsub(",", ".", logCS[,i]))
} 

##Have to be sure time and LOG_nr is collected identical
#Have small differences in number of logs, but ok


ShelfList[[ str_replace(names(All[j]), ".csv","") ]] <- ggplot(logCS) + 
  geom_point(aes(LOG_nr, Shelf1, color="Shelf1"), size=1) + #color = Diagnosis, group = Diagnosis
  geom_point(aes(LOG_nr, Shelf3, color="Shelf2"), size=1) +
  geom_point(aes(LOG_nr, Shelf5, color="Shelf3"), size=1) +
  scale_color_manual(values=c(Shelf1 = "#0000FF", Shelf2 = "#FF0000",
                              Shelf3 = "#228B22")) +
  ggtitle(str_replace(names(All[j]), ".csv","")) + 
  xlab("Logging event") +
  ylab("Shelf temperatures / °C") +
  labs(color="") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        axis.title=element_text(size=12), legend.position="bottom", axis.title.y=element_text(size=9))
#This is the exact same plot as above, but cannot assign from the one saved in ShelfList
RunList[["Shelf"]] <- ggplot(logCS) + 
  geom_point(aes(LOG_nr, Shelf1, color="Shelf1"), size=1) + #color = Diagnosis, group = Diagnosis
  geom_point(aes(LOG_nr, Shelf3, color="Shelf2"), size=1) +
  geom_point(aes(LOG_nr, Shelf5, color="Shelf3"), size=1) +
  scale_color_manual(values=c(Shelf1 = "#0000FF", Shelf2 = "#FF0000",
                              Shelf3 = "#228B22")) +
  ggtitle(str_replace(names(All[j]), ".csv","")) + 
  xlab("Logging event") +
  ylab("Shelf temperatures / °C") +
  labs(color="") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        axis.title=element_text(size=12), legend.position="bottom", axis.title.y=element_text(size=9))



Shelf200List[[ str_replace(names(All[j]), ".csv","") ]] <- ggplot(logCS[1:200,]) + 
  geom_point(aes(LOG_nr, Shelf1, color="Shelf1"), size=1) + #color = Diagnosis, group = Diagnosis
  geom_point(aes(LOG_nr, Shelf3, color="Shelf2"), size=1) +
  geom_point(aes(LOG_nr, Shelf5, color="Shelf3"), size=1) +
  scale_color_manual(values=c(Shelf1 = "#0000FF", Shelf2 = "#FF0000",
                              Shelf3 = "#228B22")) +
  ggtitle(str_replace(names(All[j]), ".csv","")) +  
  xlab("Logging event") +
  ylab("Shelf temperatures first 200 events / °C") +
  labs(color="") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        axis.title=element_text(size=12), legend.position="bottom", axis.title.y=element_text(size=9))

RunList[["Shelf200"]] <- ggplot(logCS[1:200,]) + 
  geom_point(aes(LOG_nr, Shelf1, color="Shelf1"), size=1) + #color = Diagnosis, group = Diagnosis
  geom_point(aes(LOG_nr, Shelf3, color="Shelf2"), size=1) +
  geom_point(aes(LOG_nr, Shelf5, color="Shelf3"), size=1) +
  scale_color_manual(values=c(Shelf1 = "#0000FF", Shelf2 = "#FF0000",
                              Shelf3 = "#228B22")) +
  ggtitle(str_replace(names(All[j]), ".csv","")) +  
  xlab("Logging event") +
  ylab("Shelf temperatures first 200 events / °C") +
  labs(color="") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        axis.title=element_text(size=12), legend.position="bottom", axis.title.y=element_text(size=9))



ProductList[[ str_replace(names(All[j]), ".csv","") ]] <- ggplot(logCS) + 
  geom_point(aes(LOG_nr, Product), size=1) + #color = Diagnosis, group = Diagnosis
  ggtitle(str_replace(names(All[j]), ".csv","")) + 
  xlab("Logging event") +
  ylab("Product temparature / °C") +
  labs(color="") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        axis.title=element_text(size=12), legend.position="bottom", axis.title.y=element_text(size=9))

RunList[["Product"]] <- ggplot(logCS) + 
  geom_point(aes(LOG_nr, Product), size=1) + #color = Diagnosis, group = Diagnosis
  ggtitle(str_replace(names(All[j]), ".csv","")) + 
  xlab("Logging event") +
  ylab("Product temparature / °C") +
  labs(color="") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        axis.title=element_text(size=12), legend.position="bottom", axis.title.y=element_text(size=9))
  
  

Product100List[[ str_replace(names(All[j]), ".csv","") ]] <- ggplot(logCS[1:100,]) + 
  geom_point(aes(LOG_nr, Product), size=1) + #color = Diagnosis, group = Diagnosis
  ggtitle(str_replace(names(All[j]), ".csv","")) +  
  xlab("Logging event") +
  ylab("Product temperature first 100 events / °C") +
  labs(color="") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        axis.title=element_text(size=12), legend.position="bottom", axis.title.y=element_text(size=9))

RunList[["Product100"]] <- ggplot(logCS[1:100,]) + 
  geom_point(aes(LOG_nr, Product), size=1) + #color = Diagnosis, group = Diagnosis
  ggtitle(str_replace(names(All[j]), ".csv","")) +  
  xlab("Logging event") +
  ylab("Product temperature first 100 events / °C") +
  labs(color="") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        axis.title=element_text(size=12), legend.position="bottom", axis.title.y=element_text(size=9))

ActualPList[[ str_replace(names(All[j]), ".csv","") ]] <- ggplot(logCS) + 
  geom_point(aes(LOG_nr, Actual_pressure), size=1) + #color = Diagnosis, group = Diagnosis
  ggtitle(str_replace(names(All[j]), ".csv","")) + 
  xlab("Logging event") +
  ylab("Actual pressure / XX") +
  labs(color="") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        axis.title=element_text(size=12), legend.position="bottom", axis.title.y=element_text(size=9))

RunList[["ActualP"]] <- ggplot(logCS) + 
  geom_point(aes(LOG_nr, Actual_pressure), size=1) + #color = Diagnosis, group = Diagnosis
  ggtitle(str_replace(names(All[j]), ".csv","")) + 
  xlab("Logging event") +
  ylab("Actual pressure / XX") +
  labs(color="") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        axis.title=element_text(size=12), legend.position="bottom", axis.title.y=element_text(size=9))

ActualPylimList[[ str_replace(names(All[j]), ".csv","") ]] <- ggplot(logCS) + 
  geom_point(aes(LOG_nr, Actual_pressure), size=1) + #color = Diagnosis, group = Diagnosis
  ggtitle(str_replace(names(All[j]), ".csv","")) + 
  xlab("Logging event") +
  ylab("Actual pressure / XX") +
  ylim(0, 250) +
  labs(color="") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        axis.title=element_text(size=12), legend.position="bottom", axis.title.y=element_text(size=9))

RunList[["ActualPylim"]] <- ggplot(logCS) + 
  geom_point(aes(LOG_nr, Actual_pressure), size=1) + #color = Diagnosis, group = Diagnosis
  ggtitle(str_replace(names(All[j]), ".csv","")) + 
  xlab("Logging event") +
  ylab("Actual pressure / XX") +
  ylim(0, 250) +
  labs(color="") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        axis.title=element_text(size=12), legend.position="bottom", axis.title.y=element_text(size=9))


IceConList[[ str_replace(names(All[j]), ".csv","") ]] <- ggplot(logCS) + 
  geom_point(aes(LOG_nr, Ice_condensor), size=1) + #color = Diagnosis, group = Diagnosis
  ggtitle(str_replace(names(All[j]), ".csv","")) +  
  xlab("Logging event") +
  ylab("Ice condensor temperature / °C") +
  labs(color="") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        axis.title=element_text(size=12), legend.position="bottom", axis.title.y=element_text(size=9))

RunList[["IceCon"]] <- ggplot(logCS) + 
  geom_point(aes(LOG_nr, Ice_condensor), size=1) + #color = Diagnosis, group = Diagnosis
  ggtitle(str_replace(names(All[j]), ".csv","")) +  
  xlab("Logging event") +
  ylab("Ice condensor temperature / °C") +
  labs(color="") +
  theme_bw() + 
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        axis.title=element_text(size=12), legend.position="bottom", axis.title.y=element_text(size=9))


pdf(paste(str_replace_all(str_replace(names(All[j]), ".csv","")," ", "_"), ".pdf", sep=""))
do.call('grid.arrange',c(RunList, ncol = 2))
dev.off()
}

##Have to define a width and height that works for the number of runs, not made automatic
#Optimized for 16 runs pdf("ShelfTAll.pdf", width=5, height=25)
#Otherwise run with pdf("ShelfTAll.pdf") and so forth
pdf("ShelfTAll.pdf", width=5, height=15)
do.call('grid.arrange', c(ShelfList, ncol = 2))
dev.off()

pdf("ShelfT200All.pdf", width=5, height=15)
do.call('grid.arrange', c(Shelf200List, ncol = 2))
dev.off()

pdf("ProductTAll.pdf", width=5, height=15)
do.call('grid.arrange', c(ProductList, ncol = 2))
dev.off()

pdf("ProductT100All.pdf", width=5, height=15)
do.call('grid.arrange', c(Product100List, ncol = 2))
dev.off()

pdf("IceConAll.pdf", width=5, height=15)
do.call('grid.arrange', c(IceConList, ncol = 2))
dev.off()

pdf("ActualPAll.pdf", width=5, height=15)
do.call('grid.arrange', c(ActualPList, ncol = 2))
dev.off()

pdf("ActualPAllylim0_250.pdf", width=5, height=15)
do.call('grid.arrange', c(ActualPylimList, ncol = 2))
dev.off()

```


## Additional
### Session information
```{r session_info}
sessionInfo()
```

### This document was processed on: 
```{r}
Sys.Date()
```

